\mytitle

### 2023-05-15 chapters/jitsynth/overview.tex
Deambiguate section labels
figures and code placement

\section{\jitsynth in a nutshell}% TODO bad name
\label{s:overview}

@@

We can solve this problem by asking the host synthesizer to search for
$C_\cc{addi32}$ in a space of candidate \minicompilers of length $k$. We
describe this space with a syntactic template, or a \emph{sketch}, as shown below:

\begin{lstlisting}[language=rosette,xleftmargin=0em,mathescape=true]
(define (compile-addi32 s)       ; Returns a list of k instruction holes, to be 
  (define dst (ebpf-insn-dst s)) ; filled with toy RISC-V instructions. Each    
  (define imm (ebpf-insn-imm s)) ; hole represents a set of choices, defined 
  (list (??insn dst imm) ...))   ; by the ??insn procedure.

(define (??insn . sf)            ; Takes as input source instruction fields and
  (define rd  (??reg sf))        ; uses them to construct target field holes. 
  (define rs1 (??reg sf))        ; ??reg and ??imm field holes are bitvector 
  (define rs2 (??reg sf))        ; expressions over sf and arbitrary constants.
  (choose*                       ; Returns an expression that chooses among  
    (rv-insn lui rd rs1 rs2 (??imm 20 sf))   ; lui, addiw,
    ...                                      ; ..., and
    (rv-insn sb  rd rs1 rs2 (??imm 12 sf)))) ; sb instructions.
\end{lstlisting}

Here, \cc{(??insn dst imm)} stands for a missing expression---a hole---that the
synthesizer needs to fill with an instruction from the toy RISC-V language. To
fill an instruction hole, the synthesizer must find an expression that computes
the value of the target instruction's fields. \jitsynth limits this expression
language to bitvector expressions (of any depth) over the fields of the source
instruction and arbitrary bitvector constants.\tighten

Given this sketch, and our correctness specification for $C_\cc{addi32}$, the
synthesizer will search the space defined by the sketch for a program that
satisfies the specification.
%
Below is an example of the resulting toy compiler from eBPF to
RISC-V, synthesized and translated to C by \jitsynth (without the
outer loop):\tighten
\lstinputlisting[language=C,xleftmargin=2em,firstline=1]{code/toy-compiler.c}%multicols=2,numbers=left,numbersep=.75em,

>>>>

\section{\jitsynth in a nutshell}% TODO bad name
\label{jitsynth:s:overview}

@@

We can solve this problem by asking the host synthesizer to search for
$C_\cc{addi32}$ in a space of candidate \minicompilers of length $k$. We
describe this space with a syntactic template, or a \emph{sketch}, as shown in \autoref{fig:example-sketch}.

In this sketch, \cc{(??insn dst imm)} stands for a missing expression---a hole---that the
synthesizer needs to fill with an instruction from the toy RISC-V language. To
fill an instruction hole, the synthesizer must find an expression that computes
the value of the target instruction's fields. \jitsynth limits this expression
language to bitvector expressions (of any depth) over the fields of the source
instruction and arbitrary bitvector constants.\tighten

Given this sketch, and our correctness specification for $C_\cc{addi32}$, the
synthesizer will search the space defined by the sketch for a program that
satisfies the specification.
%
Below is an example of the resulting toy compiler from eBPF to
RISC-V, synthesized and translated to C by \jitsynth (without the
outer loop):\tighten

\begin{minipage}{\linewidth}
\lstinputlisting[language=C,xleftmargin=2em,firstline=1]{code/toy-compiler.c}%multicols=2,numbers=left,numbersep=.75em,
\end{minipage}

\begin{figure}[h]
%\begin{minipage}{\linewidth}
\begin{lstlisting}[language=rosette,xleftmargin=0em,mathescape=true]
(define (compile-addi32 s)       ; Returns a list of k instruction holes, to be 
  (define dst (ebpf-insn-dst s)) ; filled with toy RISC-V instructions. Each    
  (define imm (ebpf-insn-imm s)) ; hole represents a set of choices, defined 
  (list (??insn dst imm) ...))   ; by the ??insn procedure.

(define (??insn . sf)            ; Takes as input source instruction fields and
  (define rd  (??reg sf))        ; uses them to construct target field holes. 
  (define rs1 (??reg sf))        ; ??reg and ??imm field holes are bitvector 
  (define rs2 (??reg sf))        ; expressions over sf and arbitrary constants.
  (choose*                       ; Returns an expression that chooses among  
    (rv-insn lui rd rs1 rs2 (??imm 20 sf))   ; lui, addiw,
    ...                                      ; ..., and
    (rv-insn sb  rd rs1 rs2 (??imm 12 sf)))) ; sb instructions.
\end{lstlisting}
%\end{minipage}
\caption{A fixed-length sketch describing the space of candidate \minicompilers for
         the eBPF \cc{addi32} instruction. \cc{(??insn dst imm)} describes a missing
         expression that the synthesizer must fill with a RISC-V instruction.}
\label{fig:example-sketch}
\end{figure}

### 2023-05-15 thesis.tex
Conclusion; make file
Fix bib/refs
Fix hyperlink over margins
figures and code placement

\usepackage{hyperref}
\def\chapterautorefname{Chapter}
\def\sectionautorefname{Section}
\def\subsectionautorefname{Section}
\def\subsubsectionautorefname{Section}

@@

%\usepackage{listings}
\usepackage[procnames]{listings}          % format code
\lstset{
  columns=fullflexible,
  keepspaces=true,
  showstringspaces=false,
  stringstyle=\slshape\color{green!40!black},
  basicstyle=\ttfamily\small,
  language=Python,
  morekeywords={*, self},
  commentstyle=\slshape\color{black!60},
  tabsize=2,
}

\lstdefinelanguage{Rust}{
  sensitive,
  morecomment=[l]{//},
  morecomment=[s]{/*}{*/},
  moredelim=[s][{\itshape\color[rgb]{0,0,0.75}}]{\#[}{]},
  morestring=[b]{"},
  alsodigit={},
  alsoother={},
  alsoletter={!},
  % keywords
  otherkeywords={=>},
  morekeywords={break, continue, else, for, if, in, loop, match, return, while},
  morekeywords={as, const, let, move, mut, ref, static, unsafe},
  morekeywords={dyn, enum, fn, impl, Self, self, struct, trait, type, use, where},
  morekeywords={crate, extern, mod, pub, super},
  morekeywords={abstract, alignof, become, box, do, final, macro,
    offsetof, override, priv, proc, pure, sizeof, typeof, unsized, virtual, yield},
  % traits
  morekeywords=[2]{Send},
  % types
  morekeywords=[3]{bool, char, f32, f64, i8, i16, i32, i64, isize, str, u8, u16, u32, u64, unit, usize, i128, u128},
}%

@@

% Fam + Madeline
Finally, I cannot emphasize how crucial the love and support from my family
has been over the past five years. My parents Shiela and Steve and my brothers
Daniel and Sammy have been a non-stop source of encouragement.
Madeline, I'll never be able to thank you enough for sticking through this whole
journey with me, but I will certainly try. Thank you for always being on my team.

@@

\pagestyle{headings}
\setcounter{page}{1}
\pagenumbering{arabic}
\renewcommand{\chaptermark}[1]{\markboth{\sc{\chaptername\ \thechapter.\ #1}}{}}
\renewcommand{\sectionmark}[1]{\markright{\sc{\thesection.\ #1}}{}}
% \listoftodos
\input{chapters/intro}
\input{chapters/jitsynth/jitsynth}
\input{chapters/depsynth/depsynth}

\clearpage
\addcontentsline{toc}{chapter}{Bibliography}
\singlespacing
\bibliographystyle{alpha}
\bibliography{references}

>>>>

%\usepackage{hyperref}
\def\chapterautorefname{Chapter}
\def\sectionautorefname{Section}
\def\subsectionautorefname{Section}
\def\subsubsectionautorefname{Section}

@@

%\usepackage{listings}
\usepackage[procnames]{listings}          % format code
%\lstset{
%  columns=fullflexible,
%  keepspaces=true,
%  showstringspaces=false,
%  stringstyle=\slshape\color{green!40!black},
%  basicstyle=\ttfamily\small,
%  language=Python,
%  morekeywords={*, self},
%  commentstyle=\slshape\color{black!60},
%  tabsize=2,
%}
%
%\lstdefinelanguage{Rust}{
%  sensitive,
%  morecomment=[l]{//},
%  morecomment=[s]{/*}{*/},
%  moredelim=[s][{\itshape\color[rgb]{0,0,0.75}}]{\#[}{]},
%  morestring=[b]{"},
%  alsodigit={},
%  alsoother={},
%  alsoletter={!},
%  % keywords
%  otherkeywords={=>},
%  morekeywords={break, continue, else, for, if, in, loop, match, return, while},
%  morekeywords={as, const, let, move, mut, ref, static, unsafe},
%  morekeywords={dyn, enum, fn, impl, Self, self, struct, trait, type, use, where},
%  morekeywords={crate, extern, mod, pub, super},
%  morekeywords={abstract, alignof, become, box, do, final, macro,
%    offsetof, override, priv, proc, pure, sizeof, typeof, unsized, virtual, yield},
%  % traits
%  morekeywords=[2]{Send},
%  % types
%  morekeywords=[3]{bool, char, f32, f64, i8, i16, i32, i64, isize, str, u8, u16, u32, u64, unit, usize, i128, u128},
%}%

@@

% Fam + Madeline
Finally, I cannot emphasize how crucial the love and support from my family
has been over the past five years. My parents Sheila and Steve and my brothers
Daniel and Sammy have been a non-stop source of encouragement.
Madeline, I'll never be able to thank you enough for sticking through this whole
journey with me, but I will certainly try. Thank you for always being on my team.

@@

\pagestyle{headings}
\setcounter{page}{1}
\pagenumbering{arabic}
\renewcommand{\chaptermark}[1]{\markboth{\sc{\chaptername\ \thechapter.\ #1}}{}}
\renewcommand{\sectionmark}[1]{\markright{\sc{\thesection.\ #1}}{}}
% \listoftodos
\input{chapters/intro}
\input{chapters/jitsynth/jitsynth}
\input{chapters/depsynth/depsynth}
\input{chapters/concl}

\clearpage
\addcontentsline{toc}{chapter}{Bibliography}
\singlespacing
\bibliographystyle{alpha}
\bibliography{thesis,n-conf}
%\bibliography{chapters/depsynth/n-str,chapters/depsynth/n,chapters/depsynth/p,chapters/depsynth/n-conf,chapters/jitsynth/n-str,chapters/jitsynth/n,chapters/jitsynth/jitsynth,chapters/jitsynth/n-conf}
